The variability of Betelgeuse explained by surface convection

### 2024-01-29 main.tex
modified:   main.tex
v2

\section{Method}

>>>>

\section{Method: Searching for periodicities in the polarization spectra of Betelgeuse}

Betelgeuse has been observed for the last 13 years with Narval and Neo-Narval at the Telescope Bernard Lyot. These instruments measure the polarization 
over the visible spectra of Betelgeuese (390-1000 nm) with high spectral resolution (R=65000) and high polarimetric sensitivity. Despite 
this sensitivity, the signal-to-noise ratios are not sufficient to measure the weak polarization signals in the individual atomic lines of the 
spectrum. These amplitudes are today known to be of the order of $10^{-4}$ times the continuum intensity, and only excepcionnaly do they 
reach amplitudes of $10^{-3}$ the continuum. In these exceptional observations, enough photons can be accumulated per spectral bin to 
see the linear polarization signal above noise \cite{Auriere}. Most commonly, the amplitudes of linear polarization are below noise levels. In those 
occassions we have to add up the signals of thousands of lines to reduce the noise and increase the signal-to-noise ratios. This line addition 
is done through a technique called Least-Squares Deconvolution (LSD) \cite{Donati} and assumes that the linear polarization signal is similar 
in all spectral lines up to scale factors in the sampling and amplitude. This technique has been successfully used in the past to measure 
magnetic field distributions over stellar surfaces and it is now used to produce images of the brightness distributions in the photosphere 
of Betelgeuse and other red superg
